\cvsection{Employment}
\begin{cventries}
  \cventry
    {Data Engineer}
    {GroupBy Inc.}
    {Toronto}
    {Jan. 2018 -  Apr. 2018}
    {
      \begin{cvitems}
        \item {Constructed an ETL pipeline from scratch with Google Cloud, BigQuery and MySql to process terabytes of e-commerce data.}
        \item {Aggregated data by a factor of 20, reducing query cost from \$5 to 25 cents a terabyte.}
        \item {Developed REST endpoints with Node.js for an analytics dashboard to display insights of e-commerce websites data over time.}
        \item {Deployed containerized modules to Kubernetes with Docker.}
      \end{cvitems}
    }
  \cventry
    {Software Engineer}
    {Ingle International}
    {Toronto}
    {May. 2017 - Aug. 2017}
    {
      \begin{cvitems}
        \item {Developed a enterprise-level, responsive health application with over 600,000 users.}
        \item {Used a modern tech stack of React, Redux, Typescript, Sagas, Snapshot Testing and Selenium.}
      \end{cvitems}
    }
  \cventry
    {Software Engineer}
    {Tiko 3D}
    {Oshawa}
    {May. 6012 - Aug. 2016}
    {
      \begin{cvitems}
        \item {Developed a chatbot with the Wit.ai NLP machine learning API, React and Node.js to automate customer service.}
        \item {Developed the Back End with Express.js and Mongo to process and store customer queries.}
        \item {Developed a web scraper to scrape  data from KickStarter to train ChatBot. Refined data with grammer libraries.}
        \item {Developed a mass uploader to upload common questions to Zendesk.}
      \end{cvitems} 
    }
\end{cventries}
